### 2023-02-15 main.tex
ll
Try
QISM
I added the QISM

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\numberwithin{equation}{section}

\usepackage[textsize=tiny]{todonotes}

% \usepackage[notref,notcite]{showkeys}
\usepackage{xspace}
\usepackage{bibentry}
\usepackage{easybmat}

@@

\usepackage[numbers,sort&compress]{natbib}
\usepackage{hypernat}

@@

\begin{abstract}
\noindent
....
\end{abstract}

@@

[COMPUTATIONS STILL TO DO]

\section{Conclusion}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\numberwithin{equation}{section}

%\usepackage[textsize=tiny]{todonotes}

% \usepackage[notref,notcite]{showkeys}
\usepackage{xspace}
%\usepackage{bibentry}
%\usepackage{easybmat}

@@

%\usepackage[numbers,sort&compress]{natbib}
%\usepackage{hypernat}

@@

\begin{abstract}
\noindent
...
\end{abstract}

@@

\subsubsection{Quantum inverse scattering method}
We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
\begin{equation}\label{Rmatrix}
R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
\begin{equation}\label{KmatrixHAT}
\widehat{K}_{a}(x)=I+\frac{2x}{x+1}B_{L}
\begin{equation}\label{Kmatrix}
K_{a}(x)=\left((2x+3)B_{1}+(x+3)I\right)\frac{1}{(x+1)^{2}(2x+3)}
The above matrices satisfy the following equations
\item \textit{Yang-Baxter-Equation}
R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
\item \textit{Boundary-Yang-Baxter-Equation}
R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
\item \textit{Dual Boundary-Yang-Baxter-Equation}
K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
We define the following \textit{transfer matrix}
	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
where we used the double row monodromy
	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
This trasfer matrix has the following properties
	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
with $C_{1},C_{2}>0$. \\
We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
	U_{0}(x)=\begin{pmatrix}
		A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
		C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
		\vdots&\vdots&\ddots&\vdots\\
		C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{Esse}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain
	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
		1+x&0&\ldots&0\\
		0&1-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		0&0&\ldots&1-x
	K_{0}^{\Delta}=\left((2x+3)\widetilde{B}_{1}+(x+3)I\right)\frac{(1+x)^{2}(2x+3)}{(x+1)^{2}(2x+3)}=\begin{pmatrix}
		3+x&0&\ldots&0\\
		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x
Then we obtain the correspondent transfer matrix as
	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
Then we have
	T^{\Delta}(x)&=tr_{0}\left(\begin{pmatrix}
		3+x&0&\ldots&0\\
		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x
	\end{pmatrix}\begin{pmatrix}
	A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
	C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
	\vdots&\vdots&\ddots&\vdots\\
	C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
\end{pmatrix}\right)\\&=
(3+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+3)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=
Q_{2L+2}x^{2L+2}+Q_{2L+1}x^{2L+1}+Q_{2L}x^{2L}+\ldots
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
	A(x)=\sum_{k=0}^{2L+1}A^{k}x^{k}\quad D_{ii}(x)=\sum_{k=0}^{2L+1}D_{ii}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}
The coefficients that we need are the following:
	A(x)=A^{2L+1}x^{2L+1}+A^{2L}x^{2L+1}+A^{2L-1}x^{2L-1}+\ldots
where .
	A^{2L+1}=I^{tot}
	A^{2L}=I^{tot}+2e_{11}^{tot}
		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=1\,:\,j\neq i}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
While, $\forall i=2,\ldots,N$

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}=&2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
	\end{split}
\end{equation}

%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
	B_{j}^{2L-1}=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

\begin{align}
	Q_{2L+2}&=A^{2L+1}-D_{22}^{2L+1}-D_{33}^{2L+1}\\
	Q_{2L+1}&=2A^{2L+1}+A^{2L}-D_{22}^{2L}-D_{33}^{2L}\\
	Q_{2L}&=3A^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}-D_{33}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
\section{Conclusion}
